### 2010-06-04 doc/manuals/user_interface/ui-job.tex
Added description of sort options to arcstat

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{name}&explicitly select or reject a specific site\\
%   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
%   \texttt{-i, --index}& \textit{url} &URL of an index service\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

>>>>

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{name}&explicitly select or reject a specific site\\
%   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
%   \texttt{-i, --index}& \textit{url} &URL of an index service\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-S, --sort}& \textit{criterion} & sort jobs according to jobid, submissiontime or jobname\\
   \texttt{-R, --rsort}& \textit{criterion} & reverse sorting of jobs according to jobid, submissiontime or jobname\\

   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

Jobs can be sorted according to the \texttt{jobid},
\texttt{submissiontime} or \texttt{jobname}, either in normal or
reverse order. By using the \verb#--sort# or \verb#--rsort# option
followed by the desired ordering (\texttt{jobid},
\texttt{submissiontime} or \texttt{jobname}), jobs will be sorted in
normal or reverse order. Note that the options \verb#--sort# and
\verb#--rsort# cannot be used at the same time.
